\documentclass{../styles/resume}

\begin{document}

\populatedtitle

\section{Summary}
    Software Engineer with 4+ years of hands-on experience in production support, Python integration development, and incident troubleshooting across software and infrastructure. Strong customer-facing communication, clear escalation practices, and proven collaboration with cross-functional technical teams. Comfortable with Windows-based environments, SQL workflows, rotating 12-hour night shifts, on-call support, and travel for customer/site support.

\section{Technical Skills}
\resumesublistbegin
    \item \textbf{Programming \& Scripting:} Python, JavaScript, Batch, Shell
    \item \textbf{Operating Systems:} Windows, Linux, macOS
    \item \textbf{Databases \& Data:} SQL, relational database workflows, data transformation, integration pipelines
    \item \textbf{Systems \& Networking:} Production service troubleshooting, TCP/IP and application-layer analysis, server/client issue isolation, virtualization (VirtualBox, VMware)
    \item \textbf{Support \& Collaboration:} Second-level style technical support, incident triage/escalation, cross-functional communication, technical documentation
\resumesublistend

\section{Professional Experience}

\subsectionpositiondate
    {Independent Technical Consultant}
    {Support Engineer (Contract)}
    {2024 - Present}
\resumesublistbegin
    \item Provide second-level technical support for cloud infrastructure and embedded systems clients under consulting engagement.
    \item Troubleshoot production issues across Windows and Linux environments, including database connectivity (PostgreSQL, SQLite), network configurations, and application-layer problems.
    \item Perform remote diagnostics and system health checks for distributed services; document incident resolution procedures for client handoff.
    \item Support client integration testing and quality assurance activities for backend services written in Python and Rust.
    \item Maintain rotating on-call availability for critical customer escalations; coordinate with engineering teams to resolve complex technical issues.
    \item Travel to client sites for on-site troubleshooting and system validation as needed.
\resumesublistend

\subsectionpositiondate
    {MobileCoin}
    {Software Engineer}
    {Fall 2021 - 2023}
\resumesublistbegin
    \item Developed Python integration software to connect systems and automate operational workflows.
    \item Co-managed multiple production services, monitored reliability, and resolved incidents to reduce service disruption.
    \item Delivered second-level style technical support by triaging issues, isolating root causes, and communicating clear resolution and escalation steps.
    \item Partnered with engineering teams during integration and release activities to improve service stability.
    \item Worked effectively in fast-paced support environments requiring rapid troubleshooting and continuous learning.
\resumesublistend

\subsectionpositiondate
    {Forest Meta Services}
    {Software Engineer \& Cofounder}
    {Spring 2021}
\resumesublistbegin
    \item Cofounded a technology startup focused on phone technologies and social media solutions; team was acquired.
    \item Designed, integrated, and tested chatbot features with close coordination across a small engineering team.
    \item Supported rapid iteration, issue triage, and application quality testing in a high-pressure startup environment.
\resumesublistend

\subsectionpositiondate
    {Linden Landing}
    {Community Manager}
    {2022 - 2024}
\resumesublistbegin
    \item Resolved day-to-day operational issues for a diverse community using clear communication and structured problem solving.
    \item Coordinated infrastructure-related projects and support tasks across multiple stakeholders and service providers.
    \item Partnered with local nonprofits to assess needs, coordinate services, and ensure timely follow-through.
\resumesublistend

\subsectionpositiondate
    {DoorDash \& Instacart}
    {Driver}
    {2020}
\resumesublistbegin
    \item Delivered orders accurately and on schedule while maintaining strong customer communication.
    \item Handled customer issues in real time by phone and text, de-escalating disputes and driving resolution.
\resumesublistend

\section{Education}
\subsectionlocationdate
    {Bellport Senior High School}
    {Bellport, NY}
    {}

\end{document}