\documentclass{../styles/cv}

\begin{document}

\populatedtitle

\section{Skills}
\resumesublistbegin
    \item \textbf{Communication \& Analysis:} Customer-facing support with proven ability to explain technical concepts clearly; cross-functional collaboration and team coordination in fast-paced environments; documentation and reporting skills developed through engineering and community management roles.
    \item \textbf{Security \& Investigation:} Deep interest in defensive and offensive security; hardening and configuration of Windows, Linux and Mac; troubleshooting and incident response with systematic approach to identifying root causes.
    \item \textbf{Systems \& Infrastructure:} Cloud infrastructure, virtualization; network protocols analysis, TCP/IP and application layer analysis; Python scripting for automation, control and system management.
    \item \textbf{Programming Languages:} Python (integration software, automation, scripting), JavaScript, batch and shell scripting.
    \item \textbf{Database \& Data:} SQL, database systems, data transformation and cleaning workflows.
    \item \textbf{Development Tools:} Git/GitHub, version control, pull request workflows, code review processes.
    \item \textbf{Systems \& APIs:} RESTful APIs, production service management, system troubleshooting, automation.
    \item \textbf{Operating Systems:} Linux (command line proficiency), Windows, MacOS.
    \item \textbf{Additional Technologies:} Virtualization (VirtualBox, VMware), networking protocols, hardware configuration.
\resumesublistend

\section{Professional Experience}

\subsectionpositiondate
    {MobileCoin}
    {Software Engineer}
    {2021 - 2023}
\resumesublistbegin
    \item Developed integration software in Python to connect multiple systems and automate data workflows.
    \item Co-managed several production services, monitoring performance and resolving issues to ensure system reliability.
    \item Collaborated with cross-functional teams to build mobile applications, participating in code reviews and technical discussions.
    \item Provided engineering support across the organization, quickly learning new systems and troubleshooting technical problems.
    \item Worked in fast-paced environment requiring adaptability and continuous learning of emerging technologies.
\resumesublistend

\subsectionpositiondate
    {Forest Meta Services}
    {Software Engineer \& Cofounder}
    {2021}
\resumesublistbegin
    \item Cofounded a phone technologies and social media startup; team was successfully acquired.
    \item Designed, tested, and refined chatbot algorithms, working with conversational AI and natural language processing.
    \item Collaborated closely with small engineering team using agile methodologies and rapid iteration cycles.
    \item Gained experience with API development and integration in a startup environment with limited resources.
    \item Worked in high pressure startup environment requiring quick decision-making and technical flexibility.
\resumesublistend

\section{Key Strengths}
\resumesublistbegin
    \item \textbf{Strong Fundamentals:} Solid foundation in Python, SQL, and software engineering best practices with hands-on production experience.
    \item \textbf{Fast Learner:} Proven ability to quickly understand complex technical systems and adapt to new technologies.
    \item \textbf{Collaborative:} Experience working across teams and organizations with strong communication skills and willingness to ask questions.
    \item \textbf{Detail-Oriented:} Demonstrated attention to detail through troubleshooting production systems and maintaining code quality.
\resumesublistend

\section{Interests}
\resumesublistbegin
    \item \textbf{Blockchain \& Crypto:} Passionate about decentralized technologies and actively learning about blockchain architecture, smart contracts, and the Web3 ecosystem.
    \item \textbf{Data Engineering:} Interest in building scalable data pipelines and transforming raw data into actionable insights.
    \item \textbf{Continuous Learning:} Self-driven learner with curiosity for emerging technologies; regularly explore new programming languages, frameworks, and development practices.
\resumesublistend

\end{document}
