\documentclass{../styles/coverletter}

\begin{document}

\populatedtitle





February 27, 2026\newline
Hiring Manager\\
Dematic\\[4pt]
	\textbf{Software Engineer, Technical Support -- Night Shift}\newline


Dear Hiring Manager,\newline


I am writing to apply for the Software Engineer, Technical Support -- Night Shift position at Dematic. I offer hands-on experience supporting production systems, developing Python integration software, and troubleshooting software and infrastructure issues in fast-paced environments.\newline

Currently, I provide second-level technical support for cloud infrastructure and embedded systems clients as a contract Support Engineer. I troubleshoot production issues across Windows and Linux environments, including database connectivity (PostgreSQL, SQLite), network configurations, and application-layer problems. I perform remote diagnostics and system health checks for distributed services, support integration testing and quality assurance for backend services, and maintain rotating on-call availability for critical customer escalations. I regularly travel to client sites for on-site troubleshooting and system validation.\newline

Previously at MobileCoin, I developed integration software and co-managed production services, monitoring reliability, resolving incidents, and communicating clear remediation steps across technical teams. This combined experience aligns closely with Dematic's second-level support model and its emphasis on cross-functional coordination with project, development, and technical engineers.\newline

I work effectively across operating systems and technical environments, including Windows-based workflows, SQL-driven data processes, and network-aware troubleshooting. My experience with Oracle and MS SQL databases, along with server hardware and Ethernet network troubleshooting, directly matches the technical requirements outlined in your position.\newline

I am fully prepared for rotating 12-hour night shifts, on-call responsibilities, and travel to customer locations as needed. I bring a calm, service-oriented approach to high-pressure support work and a consistent focus on restoring and maintaining reliable operations.\newline

Thank you for your consideration. I would welcome the opportunity to contribute to Dematic's Global Software Organization and deliver responsive, high-quality technical support to your customers.\newline



Sincerely,\newline

Zoey Drapal

\end{document}