\documentclass{../styles/coverletter}

\begin{document}

\populatedtitle




 
March 17, 2026\newline
Hiring Manager\\
Deloitte\\[4pt]
\textbf{Full-Stack Software Engineer --- CL4 (Platforms)}\newline


Dear Hiring Manager,\newline


I am writing to apply for the Full-Stack Software Engineer (CL4) position on Deloitte's Product Engineering Platforms team. With 12+ years of hands-on technical leadership delivering outcome-driven, cloud-native solutions, I am confident I can contribute immediately to Deloitte's mission of delivering with excellence.\newline

My experience maps directly to the responsibilities you describe. At Superior Technologies Research, I served as lead full-stack developer across two simultaneous client engagements: I architected and delivered an enterprise HR platform in a SAFe environment---establishing SLOs, SRE-aligned observability with OpenTelemetry, and full-stack delivery from design through Kubernetes production deployment. In parallel, I led a legacy platform modernization, where I built the technical and business case to adopt claims-based access control (CBAC) over a simpler RBAC approach, persuading stakeholders by clearly articulating audit hardening requirements and future-proofing benefits. I also spearheaded a cross-organizational security initiative, designing the solution, coordinating implementation with multiple team leads, and driving adoption of better testing and code standards through pair programming and measurable coverage metrics.\newline

Across my career I have shipped production software in C\#/.NET, Go, TypeScript, React, Angular, Node.js, Java, and Python, with cloud-native deployments on AWS, Azure, and GCP. I practice DevSecOps daily: SonarQube quality gates, PR-enforced CI/CD, and automated test coverage as a first-class delivery signal. I hold a B.S. in Computer Science from Michigan Technological University.\newline

I am drawn to Deloitte's emphasis on outcome accountability, cross-functional co-creation, and continuous engineering craftsmanship---values I have built my career around. I would welcome the opportunity to bring that same hands-on, delivery-focused approach to your team.\newline

Thank you for your time and consideration.\newline



Sincerely,\newline

Marvin Kassabian

\end{document}
