\documentclass{../styles/resume}

\begin{document}

\populatedtitle

\section{Summary}
    Senior Software Engineer with 12+ years of hands-on technical leadership delivering outcome-driven solutions across full-stack, cloud-native, and platform engineering at enterprise scale. Proven advocate for code integrity and customer outcomes; expert in team mentoring, XP practices (pair programming, continuous integration discipline), and persuading stakeholders on complex technical trade-offs. Demonstrated success across C\#/.NET, JavaScript/TypeScript, Go, Python, and React, with deep expertise in microservices architecture, AI/ML integration, DevSecOps delivery pipelines, and rapid domain expertise acquisition. Leads cross-functional teams in outcome-focused environments (Agile, SAFe) on AWS, Azure, and GCP.

\section{Technical Skills}
\resumesublistbegin
    \item \textbf{Core Stack:} C\#, .NET, ASP.NET Core, JavaScript/TypeScript, Go, Python, React, Angular, Node.js, Java, REST APIs, SQL/NoSQL
    \item \textbf{Delivery:} Platform Engineering, Full-Stack Feature Delivery, Microservices, Legacy Modernization, Automated Testing, CI/CD Pipelines, DevSecOps, SonarQube, SRE, Agile, SAFe, Code Reviews, Git
    \item \textbf{Platform \& Cloud:} Docker, Kubernetes, AWS, Azure, GCP, GitHub Actions, Azure DevOps, OpenTelemetry, Claims-Based Access Control, Secure Integrations, GenAI, AI/ML (TensorFlow, scikit-learn, Whisper, Hugging Face)
\resumesublistend

\section{Professional Experience}

\subsectionpositiondate
    {Superior Technologies Research}
    {Senior Software Contractor}
    {May 2025 - February 2026}
\resumesublistbegin
    \item Led cross-organizational security initiative: designed critical security patch, coordinated implementation across multiple team leads, conducted pair programming sessions, and established test coverage metrics to validate completeness—demonstrating technical leadership and collaborative influence.
    \item Architected and delivered outcome-driven HR platform in SAFe, establishing SLOs for availability and response time, then systematically reduced downtime through service observability (OpenTelemetry) and health-driven alerting aligned with SRE principles.
    \item Served as technical advocate for platform integrity and customer outcomes, leading requirement analysis, component design, and full-stack delivery (TypeScript/Vue.js frontend, Go REST APIs) from design through production deployment on Kubernetes.
    \item Modernized legacy platform: persuaded stakeholders to adopt claims-based access control (CBAC) over RBAC by articulating audit hardening and future-proofing benefits despite upfront cost; migrated CI/CD to Azure DevOps, established SonarQube quality gates, and enforced DevSecOps practices with PR-gated testing.
    \item Demonstrated cross-functional collaboration and communication through frontend migration (Bootstrap→Vue.js/Inertia.js), GenAI voice agent integration, and Whisper + Hugging Face knowledge pipeline converting training materials into searchable, timestamped references.
\resumesublistend

\subsectionpositiondate
    {Calder Solutions}
    {Part-Time Software Developer}
    {July 2024 - August 2025}
\resumesublistbegin
    \item Built customer-facing web applications in React (Next.js/TypeScript) and Angular, integrated with custom ASP.NET Core (C\#) backend services; maintained a legacy Java application for one client through a full-stack replacement.
    \item Delivered full-stack feature work across admin and e-commerce flows, collaborating with product and design partners to translate business requirements into production-ready UI and API behavior.
    \item Participated in code reviews and production support across multiple client systems, resolving defects quickly to maintain uptime and service expectations.
\resumesublistend

\subsectionpositiondate
    {Superior Technologies Research}
    {Senior Software Contractor}
    {September 2021 - March 2024}
\resumesublistbegin
    \item Delivered microservice and frontend enhancements in a SAFe environment, decomposing legacy systems into maintainable services with Go REST APIs and Vue.js.
    \item Built integration APIs and an AWS event bus using SQS/EventBridge to connect distributed systems reliably.
    \item Applied TDD practices, expanded automated test coverage, and documented operational standards to support consistent deployments, environmental readiness, and cross-team handoff.
\resumesublistend

\subsectionpositiondate
    {eoStar}
    {Software Developer}
    {February 2016 - September 2021}
\resumesublistbegin
    \item Developed and maintained cross-platform point-of-sale applications in C\# for desktop and Xamarin.iOS mobile, supporting beverage distributors and retailers including Meijer.
    \item Built and maintained ASP.NET Core (C\#) REST APIs for third-party and government integrations, delivering scalable production-ready services in an Agile environment.
    \item Deployed TensorFlow-based machine learning models on iOS for intelligent order suggestions and voice assistant features, optimizing inference for mobile environments.
    \item Shipped production sales and delivery workflow enhancements across mobile and desktop platforms, including defect resolution and field support.
\resumesublistend

\section{Education}
\subsectiondate
    {Michigan Technological University}
    {September 2011 - December 2015}
\begin{adjustwidth}{1em}{0pt}
    {B.S. in Computer Science, Minor in Mathematics}
\end{adjustwidth}

\end{document}