\documentclass{../styles/coverletter}

\begin{document}

\populatedtitle

August 7, 2024\newline

Michigan Immigrant Rights Center\\
1500 E. Beltline SE, Suite 300\\
Grand Rapids, MI 49506\newline

Dear Hiring Manager at the Michigan Immigrant Rights Center,\newline

I am writing to express my interest in the Data Coordinator for Immigrant Children position.\newline

I have always aspired to use my technical background to support causes that matter to me, and MIRC's goals, work, and pillars deeply resonate with me. Although I have not worked in the legal field, over the past three years since moving back to Michigan, I have actively engaged with my community through local activism, supporting striking workers, and assisting my unhoused neighbors through mutual aid groups. I am eager to apply this same passion and commitment to my professional work.\newline

With over a decade of experience as a software developer, I bring a strong technical background to this role. My experience includes analyzing data at eoStar, using Python’s scikit-learn library to understand purchasing habits of suppliers and customers, and managing data to ensure it is clean, easy to understand, and sanitized. While I have not used R professionally, I became proficient with it during my college machine learning classes. My greatest skill in software development is the ability to quickly acquire and apply new skills as needed.\newline

I am confident that my technical expertise and commitment to social justice would make me a great addition to the Michigan Immigrant Rights Center.\newline

Thank you for considering my application,

Marvin Kassabian

\end{document}
