\documentclass{../styles/custom}

\begin{document}

\resumeheadersimple
    {Marvin Lincoln Kassabian}
    {marvin.kassabian@gmail.com}
    {+1 (616) 916-5415}

\section{Education}
\subsectionlocationdate
    {Michigan Technological University}
    {B.S. in Computer Science, Minor in Mathematics}
    {2015}

\section{Skills}
\resumesublistbegin
    \item \textbf{Programming Languages:} Go, Java, \cpp, C\#, TypeScript, Python, Ruby, R
    \item \textbf{Frameworks and Libraries:} Next.js, Vue.js, Angular, React, scikit-learn
    \item \textbf{Databases:} PostgreSQL, T-SQL, MongoDB, Firebase
\resumesublistend

\section{Professional Experience}

\subsectionpositiondate
    {Calder Solutions}
    {Part-Time Software Developer}
    {July 2024 - Present}
\resumesublistbegin
    \item Developed the frontend of an educational platform using Next.js, enabling teachers to create, schedule, and publish lessons with integrated questions.
    \item Utilized PayloadCMS for managing lesson content and Firebase for handling student responses.
    \item Collaborated with the design team and incorporated customer feedback to ensure the website is user-friendly, accessible, and meets client requirements.
\resumesublistend

\subsectionpositiondate
    {Superior Technologies Research}
    {Senior Software Contractor}
    {September 2021 - March 2024}
\resumesublistbegin
    \item Decomposed legacy PHP and ASP.NET monolith codebase into domain-specific Go services with a Vue.js frontend.
    \item Utilized Ginkgo and Gomega to ensure that transitioning from a monolith to domain-specific services maintained feature parity, adhering to Test-Driven Development (TDD) principles.
    \item Created a Go-based API to streamline accounts payable integration between Medius and Microsoft Dynamics GP, utilizing calls to the Medius API to retrieve necessary data.
    \item Created technical documentation and provided hands-on support to teams for tagged deployment process changes, including tutorials on the new deployment method.
    \item Refactored repositories to adhere to domain-driven design (DDD).
    \item Contributed to a Go library aimed at standardizing service creation, enhancing DevOps capabilities for service management.
    \item Rewrote Node.js services in Go for improved maintainability.
    \item Updated legacy codebase for multi-currency support and enhanced data security.
    \item Developed a robust expense processing integration that transforms Expensify data into consumable models.
    \item Converted legacy T-SQL stored procedures to maintainable Go code.
\resumesublistend

\subsectionpositiondate
    {eoStar}
    {Software Developer}
    {August 2016 - September 2021}
\resumesublistbegin
    \item Performed K-means clustering analysis with scikit-learn to identify customer segments and purchasing patterns, providing actionable insights for marketing and inventory strategies.
    \item Trained and evaluated a classifier for predicting purchasing behavior using scikit-learn and custom data processing, optimizing model performance through precision-recall analysis and ROC curve visualization.
    \item Built and deployed a TensorFlow-based machine learning model from sales data on end-user iOS devices.
    \item Developed a RESTful API in ASP.NET Core for daily data transfers to third-party software.
    \item Led projects involving order suggestion and voice assistant functionalities, utilizing machine learning models.
    \item Enabled tax data uploads through integration with the Zambia Revenue Authority.
    \item Designed and implemented backend systems for Zambian integration in ASP.NET Core.
    \item Collaborated with a third-party team to resolve data ingestion issues by assisting their developers with Ruby code.
    \item Supported and developed a Xamarin.iOS app to facilitate transactions for field users.
\resumesublistend

\subsectionpositiondate
    {eoStar}
    {Data Migration Specialist}
    {February 2016 - August 2016}
\resumesublistbegin
    \item Performed ETL (Extract, Transform, Load) operations to integrate databases from newly acquired clients into the company system using T-SQL.
    \item Enhanced a legacy \cpp application by integrating a SQL export feature, facilitating seamless data conversion from a proprietary database system, and improving data extraction and transfer processes between client systems and our platform.
\resumesublistend

\subsectionpositiondate
    {Jackson National Life Insurance}
    {Software Developer}
    {Spring 2013 - Summer 2015}
\resumesublistbegin
    \item Led a team of three to migrate databases, troubleshoot bugs in multiple Access GUIs and databases based on end-user feedback, and deployed database migrations and fixes to production.
    \item Collaborated within a team of five to develop a Java-based application for aggregating employee hours and generating schedules.
    \item Contributed to developing an application to streamline the recruitment and hiring process.
    \item Developed a Java application in a team of four to report programmer performance to managers.
\resumesublistend

\end{document}
