\documentclass{../styles/resume}

\begin{document}

\populatedtitle

\section{Summary}
    Software developer with professional experience designing, developing, and maintaining software systems, with a strong focus on security related projects. Experienced in building production grade applications, automation frameworks, and large scale data processing pipelines across Windows and cloud environments. Demonstrates applied knowledge of secure software design, Windows operating system internals, and enterprise environments such as Active Directory.

\section{Technical Skills}
\resumesublistbegin
    \item \textbf{Programming Languages:} Rust, Python, PowerShell, C\#, TypeScript
    \item \textbf{Software Development:} Backend services, automation frameworks, Windows native development, secure software design
    \item \textbf{Operating Systems and Platforms:} Windows operating system internals, enterprise Windows environments, Active Directory
    \item \textbf{Infrastructure \& Automation:} AWS, CloudFormation, CI/CD pipelines, Docker, GitHub Actions
    \item \textbf{Data Systems:} ETL pipelines, distributed data processing, SQL and NoSQL databases
    \item \textbf{Web Development:} React, TypeScript, web based administration and management interfaces
\resumesublistend

\section{Professional Experience}

\subsectionpositiondate
    {Independent Contractor}
    {Software Developer (Security Focused Projects)}
    {October 2024 - Present}
\resumesublistbegin
    \item Designed, developed, and maintained software systems supporting security related projects, including internal tooling, automation frameworks, and data processing platforms.
    \item Developed backend services and automation pipelines for large scale ingestion, processing, and indexing of open source intelligence data.
    \item Designed and implemented Windows native software using PowerShell and C\#, including command line tooling and automation frameworks.
    \item Built web based administration and management interfaces for monitoring and controlling data processing workflows.
    \item Implemented cloud based infrastructure and automation using AWS services including EC2, VPC, and CloudFormation.
    \item Built a comprehensive PowerShell framework to fully automate purple team engagements for customers.
    \item Contributed software enhancements, bug fixes, and feature implementations to widely used open source security tools written in Python and C\#.
    \item Designed and built a distributed data processing platform for indexing and querying large volumes of structured and unstructured data.
\resumesublistend

\subsectionpositiondate
    {Xederif Inc}
    {Software Engineering Intern}
    {Winter 2023 - Summer 2024}
\resumesublistbegin
    \item Implemented and maintained integrated software components primarily in Python with contributions in JavaScript and Rust.
    \item Scoped deliverables directly with executives and managed expectations for production services.
    \item Maintained on-call rotation for production triage and incident response.
    \item Applied application hardening and service isolation practices using EKS/Kubernetes with GitOps workflows.
    \item Established observability with DataDog logging and PagerDuty alerting infrastructure.
\resumesublistend

\section{Projects}

\subsectiondate
    {USRBG - Discord Profile Banner Service}
    {Ongoing}
\resumesublistbegin
    \item Designed, developed, and operates a popular, free, web based software service and plugin ecosystem for Discord client modifications.
    \item Responsible for the full software development lifecycle, including backend service development, data storage design, asset processing, and web based administration interfaces.
    \item Designed and implemented scalable infrastructure to support a large active user base, delivering hundreds of gigabytes of image assets and handling terabytes of data transfer per month.
    \item Development responsibilities include performance optimisation, storage management, reliability improvements, and secure operation of the platform.
\resumesublistend

\section{Education}
\subsectionlocationdate
    {Pioneer High School}
    {Ann Arbor, Class of 2023}
    {Graduated 2023}

\end{document}